Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-13 Paper/gammaRays.tex
Corrections to parameter fit

First of all, we need to determine, which parameters to fit. At most, the observables of a particular burst depend on 10 parameters: 8 of the burst $\left(\gamma, \eta_0, r_0, n, \omega_0, \theta_0, k, \alpha\right)$, and 2 of the observer $\left(z, \chi\right)$. However, some of these parameters only change observables trivially, and, also, there are transformations of variables, which will not change observables at all (see equation \ref{eq:p}):
\begin{itemize}
	\item{The number of photons $p$ depends linearly on $\eta_0$, so $\eta_0$ doesn't affect other observables like duration, or stretching factor. We can easily fit $\eta_0$ to match the observed photon count.}
	\item{If we make a simultaneous transformation of $r_0 \rightarrow \lambda r_0$ and $\eta_0 \rightarrow \frac{1}{\lambda^3}\eta_0$, where $\lambda$ is a parameter of transformation, then only the duration of the burst will change. Other observables, like the total number of photons, or stretching factor, will not be affected.}
	\item{Finally, if we make a following transformation: $\omega_0 \rightarrow \lambda \omega_0$, $\theta_0 \rightarrow \lambda^k \theta_0$, $\eta_0 \rightarrow \lambda^\alpha \eta_0$, where $\lambda$ is another transformation parameter, no observables will change whatsoever.}
\end{itemize}
Given these transformations, we can reduce the number of parameters for fit to 7: $\left(\gamma, n, \theta_0, k, \alpha, z, \chi\right)$.

Also, some of the parameters we know from observations:
\begin{itemize}
	\item{Redshifts $z$ of many bursts have been measured \cite{Ackermann:2013zfa}.}
	\item{We know that relativistic factors $\gamma$ are on the order of magnitude\footnote{Our minimization procedure can find similar minimums for other values of $\gamma$, at least from $100$ to $1000$} of $\gamma = 300$ \cite{Ghirlanda:2011ux}.}
\end{itemize}
This knowledge allows us to reduce the number of parameters to minimize against to just 5: $\left(n, \theta_0, k, \alpha, \chi\right)$.

@@

\begin{figure}
	\hspace*{\fill}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionHistogram}
		\label{fig:kappaDistributionHistogram}
		\caption{Histogram (blue) obtained from the model. Bar lines (black) show observed stretching factors.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionCDF}
		\label{fig:kappaDistributionCDF}
		\caption{CDF (blue) obtained from the model. Gray curve and bar lines show observed stretching factors.}
	\end{subfigure}
	\hspace*{\fill}
	\caption{Stretching factors histogram and CDF produced by our model. The sample contains $4096$ bursts.}
	\label{fig:kappaDistribution}
\end{figure}

>>>>

First of all, we need to determine, which parameters to fit. At most, the observables of a particular burst depend on 10 parameters: 8 of the burst $\left(\gamma, \eta_0, r_0, n, \omega_0, \theta_0, k, \alpha\right)$, and 2 of the observer $\left(z, \chi\right)$. However, some of these parameters only change observables trivially, and, also, there are transformations of variables, which will not change observables at all (see equation \ref{eq:p}):
\begin{itemize}
	\item{The number of photons $p$ depends linearly on $\eta_0$, so $\eta_0$ doesn't affect other observables like duration, or stretching factor. We can easily fit $\eta_0$ to match the observed photon count.}
	\item{If we make a simultaneous transformation of $r_0 \rightarrow \lambda r_0$ and $\eta_0 \rightarrow \frac{1}{\lambda^3}\eta_0$, where $\lambda$ is a parameter of transformation, only duration of the burst will change. Other observables, like the total number of photons, or stretching factor, will not be affected.}
	\item{Finally, if we make a following transformation: $\omega_0 \rightarrow \lambda \omega_0$, $\theta_0 \rightarrow \lambda^k \theta_0$, $\eta_0 \rightarrow \lambda^\alpha \eta_0$, where $\lambda$ is another transformation parameter, no observables will change whatsoever.}
\end{itemize}
Given these transformations, we can reduce the number of parameters for fit to 7: $\left(\gamma, n, \theta_0, k, \alpha, z, \chi\right)$.

Also, some of these parameters we know from observations:
\begin{itemize}
	\item{Redshifts $z$ of many bursts have been measured \cite{Ackermann:2013zfa}.}
	\item{We know that relativistic factors $\gamma$ are on the order of magnitude\footnote{Our minimization procedure can find similar minimums for other values of $\gamma$, at least from $100$ to $1000$} of $\gamma = 300$ \cite{Ghirlanda:2011ux}.}
\end{itemize}
This knowledge allows us to reduce the number of parameters to minimize against to just 5: $\left(n, \theta_0, k, \alpha, \chi\right)$.

@@

\begin{figure}
	\hspace*{\fill}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionHistogram}
		\label{fig:kappaDistributionHistogram}
		\caption{Histogram (blue) obtained from the model. Black error bars show observed stretching factors.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionCDF}
		\label{fig:kappaDistributionCDF}
		\caption{CDF (blue) obtained from the model. Gray curve and black error bars show observed stretching factors.}
	\end{subfigure}
	\hspace*{\fill}
	\caption{Stretching factors histogram and CDF produced by our model. The sample contains $4096$ bursts.}
	\label{fig:kappaDistribution}
\end{figure}
